%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

\begin{document}
\begin{minipage}[t]{1\textwidth} % 45% of the page width for name
    \vspace{-\baselineskip} % Required for vertically aligning minipages
    
    % If your name is very short, use just one of the lines below
    % If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
    \colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Kiron Roy}}}}} \hspace{.3 cm} \large\texttt{732-241-1722\slashsep\href{mailto:kroy.xc@gmail.com}{kroy.xc@gmail.com}\slashsep\href{https://github.com/kroy}{github.com/kroy}}
    
    \vspace{6pt}
    
    %{\huge Web App Architect} % Career or current job title
\end{minipage}

\vspace{0.5cm}

\parbox{1\textwidth}{To whom it may concern,}\\
\vspace{0.5cm}\\
\parbox{1\textwidth}{\hspace{0.75cm}A few years after 9/11, as Haliburton and the TSA were introducing their millimeter wave scanners to the travelling public, I started noticing the topic of airport security coming up strangely often at family gatherings. “Make sure you get to the airport extra early,” my Indian family members would joke, “just in case you get randomly selected for an extra screening.” We’d all laugh, yet somehow my family, which has never had a reputation for punctuality, started showing up early for flights.}\\
\vspace{0.25cm}\\
\parbox{1\textwidth}{\hspace{0.75cm}Despite our concerns, we really didn’t have much to worry about. We weren’t at risk of deportation, violence, or even anything more than a three minute pat-down and swab. Still, it felt wrong, and it made me more receptive to the idea that servants of justice aren’t blind, that they might have forgotten to tare the kitchen scales of justice. Why else would I, with my light skin and American mannerisms, slip through security un-examined, while my father was selected almost every time?}\\
\vspace{0.25cm}\\
\parbox{1\textwidth}{\hspace{0.75cm}Meanwhile, I went off to college, got a CS degree and a couple of jobs, blissfully free of major legal issues or fears that a minor brush with the law would turn deadly. I was able to explore my curiosity and build my technical skills. I developed into a versatile software engineer comfortable diving into a problem, asking questions, and learning something new. I have opinions, but I’m not dogmatic. I’m optimistic, but with a healthy dose of skepticism. I love hearing perspectives that are different from mine.}\\
\vspace{0.25cm}\\
\parbox{1\textwidth}{\hspace{0.75cm}When I started at Etsy in 2014, it was the height of the golden age of data. We felt like anything and everything could be solved with data. It was a pretty unrefined perspective, to be frank. You might use data to A/B test yourself into the perfect color for a specific button, but it takes a much more sophisticated method to move past a local maximum, and to understand how users interact with your website at a more macro level. Not to mention that data isn’t going to tell you if a color-blind person can even read the text on your optimally-colored button.}\\
\vspace{0.25cm}\\
\parbox{1\textwidth}{\hspace{0.75cm}Nevertheless, this fascination with data pushed advances in the art of moving, parsing, and storing huge amounts of data, both at Etsy and in the tech industry in general. And there were times when all that machinery facilitated some amazing insights. I learned to temper my enthusiasm for data for its own sake. I started to understand that watching a graph go up is not the same as making something meaningful change.}\\
\vspace{0.25cm}\\
\parbox{1\textwidth}{\hspace{0.75cm}Everything I’ve heard about the Center for Policing Equity indicates that you’ve already reached that conclusion. Data-collection, and its attendant technologies, is one tool among many to be used to solve a problem. Data on how and when police use force is important to collect and analyse. But so is understanding the subjective experience of people who feel threatened by members of service. I’d like to work with you and apply my experience as an engineer to make daily life a bit more livable for people whose unpleasant run-ins with the institutions of justice aren’t confined to the airport security line.}\\
\vspace{0.5cm}\\

\parbox{1\textwidth}{Sincerely,\\Kiron Roy}

\end{document}