%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%   TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{1\textwidth} % 45% of the page width for name
    \vspace{-\baselineskip} % Required for vertically aligning minipages
    
    % If your name is very short, use just one of the lines below
    % If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
    \colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Kiron Roy}}}}} \hspace{.3 cm} \large\texttt{732-241-1722\slashsep\href{mailto:kroy.xc@gmail.com}{kroy.xc@gmail.com}\slashsep\href{https://github.com/kroy}{github.com/kroy}}
    
    \vspace{6pt}
    
    %{\huge Web App Architect} % Career or current job title
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%   INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{About Me}

\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
    \vspace{-\baselineskip} % Required for vertically aligning minipages
    
    I'm a web developer with wide ranging experience over 7 years in the industry. I've spent the bulk of my time at Etsy and Handy, where I worked all over the stack, from server configuration, to DB schemas, to the frontend. I'm looking for a job that'll help build a better future.
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
    \vspace{-\baselineskip} % Required for vertically aligning minipages
    \icon{Qrcode}{12}{\textbf{Programming Langs} Ruby, php, Javascript}\\
    \icon{InternetExplorer}{12}{\textbf{Web} Rails, React}\\
    \icon{Database}{12}{\textbf{Datastores} MySQL, some Hive and Vertica}\\
    \icon{GraduationCap}{12}{\textbf{Education} BA in CS and Math, Oberlin College, 2011}
\end{minipage}

% \begin{center}
%     \bubbles{5/Eclipse, 6/git, 4/Office, 3/Inkscape, 3/Blender}
% \end{center}

%----------------------------------------------------------------------------------------
%   EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
     \entry
        {Handy}
        {Software Engineer\hspace{1mm}\texttt{Rails}}
        {Sep 2019 -- Present}
        {
            Full-stack Rails development on the micro-services powering Handy.com and the Handy mobile apps\\
            Fast-paced, iterative feature implementation; continuous deployment; ownership after launch\\
            Part of the production on call rotation; facilitated "post mortems" for incidents I handled\\
            Projects include:\\
            \begin{minipage}[t]{0.05\textwidth}\,\end{minipage}
            \begin{minipage}[t]{0.8\textwidth}Backend work to power fixed, incremental payments to providers.\end{minipage}\\
            \begin{minipage}[t]{0.05\textwidth}\,\end{minipage}
            \begin{minipage}[t]{0.8\textwidth}A "Dedicated Provider" feature for customers and their favorite providers.\end{minipage}\\
            \begin{minipage}[t]{0.05\textwidth}\,\end{minipage}
            \begin{minipage}[t]{0.8\textwidth}A subscription service w/ discount offerings.\end{minipage}\\
            \begin{minipage}[t]{0.05\textwidth}\,\end{minipage}
            \begin{minipage}[t]{0.8\textwidth}Remediation of various non-performant queries causing outages.\end{minipage}
        }
    \entry
        {Etsy}
        {Software Engineer \hspace{1mm}\texttt{php}\slashsep\texttt{React}}
        {Aug 2014 -- Aug 2018}
        {
            Developed features for Etsy.com, working on most parts of the stack\\
            Collaborated with designers, product managers, and business stakeholders\\
            Prototyped, built and iterated on features for internal teams and Etsy Sellers, running A/B tests, analysing\\
                \begin{minipage}[t]{0.05\textwidth}\,\end{minipage}
                \begin{minipage}[t]{0.85\textwidth}user data by writing map-reduce jobs on Hadoop, responding to feedback from users, and producing tested, easily-maintainable code\end{minipage}\\
            Monitored my team's critical features on Etsy.com and responded to outages\\
            Deployed code multiple times per day\\
            Participated in post-mortems and proposed remediation items\\
            Taught non-technical teammates to access our analytical data stores\\
            Projects included:\\
            \begin{minipage}[t]{0.05\textwidth}\,\end{minipage}
            \begin{minipage}[t]{0.8\textwidth}A push-notification framework.\end{minipage}\\
            \begin{minipage}[t]{0.05\textwidth}\,\end{minipage}
            \begin{minipage}[t]{0.8\textwidth}A React app to help build marketing emails sent to millions of subscribers.\end{minipage}\\
            \begin{minipage}[t]{0.05\textwidth}\,\end{minipage}
            \begin{minipage}[t]{0.8\textwidth}Implementing Canada Post shipping labels for Etsy Sellers.\end{minipage}\\
            \begin{minipage}[t]{0.05\textwidth}\,\end{minipage}
            \begin{minipage}[t]{0.8\textwidth}Rearchitecture of the pre-calculated shipping interface.\end{minipage}
        }
    \entry
        {Freelance}
        {Web Developer \hspace{1mm}\texttt{php}\slashsep\texttt{js}}
        {Jan 2014 - Aug 2014}
        {
            Worked with clients to design, build, deploy, and maintain websites and webapps\\
        }
    \entry
        {Accenture}
        {Java Engineer \hspace{1mm}\texttt{Java}\slashsep\texttt{Spring}}
        {2012 -- May 2013}
        {
            Developed web applications for government clients\\
            Supported post-production operations and maintenance of high-demand, high-availability websites\\
        }
\end{entrylist}

%----------------------------------------------------------------------------------------
%   ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------
\cvsect{References}

    \large\textbf{Bertrand Moulard} \slashsep \large\texttt{Manager at Etsy\slashsep917 214 0977\slashsep\href{mailto:bertrandmoulard@gmail.com}{bertrandmoulard@gmail.com}}\\
    \large\textbf{David Leibovic} \slashsep \large\texttt{Coworker at Etsy\slashsep804 3499548\slashsep\href{mailto:david.leibovic@gmail.com}{david.leibovic@gmail.com}}\\
    \large\textbf{Michelle Miller} \slashsep \large\texttt{Founder at coworker.org\slashsep\href{mailto:michelle@coworker.org}{michelle@coworker.org}}

%----------------------------------------------------------------------------------------

\end{document}
